%!TEX program = xelatex
\documentclass[10pt,letter]{moderncv}
\moderncvtheme[burgundy]{classic}                
%\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{tgpagella}% Latin Modern typeface (font)

\firstname{Frédéric}
\familyname{Vachon}
\title{Master's candidate in Geographical Sciences}              
\address{119, Saint-Luc street}{Quebec city (Quebec)  G1N 2R4}    
\mobile{581~998~6179}                    
\email{frederic.vachon.1@ulaval.ca}
\social[linkedin]{frvachon}                       
%\homepage{www.francoistessier.info}

\begin{document}
% Letter Information 
\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
\date{\today} 
\opening{Dear Sir or Madam,} % Opening greeting
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
\begin{document}
{\fancyfoot[r]{}            % No page/lastapage in the letter
\setcounter{page}{0}        % Change if letter is more than 1 page
\makelettertitle            % Print letter title
Lore ipum dolor             % Letter body
sit amet, consectetuer 
adiscipliging elit. 
Up purus ... 

\makeletterclosing          % Print letter signature
\newpage 
\maketitle

\section{Education}
\cventry{In progress}{M.Sc. in Geographical Sciences} {Université Laval}{}{}{}
\cventry{2014}{B.Sc. in Geography} {Université Laval}{}{}{Concentration : Human and historical geography}
\cventry{2011}{Certificate in sociology}{Université laval}{}{}{}
\cventry{2010}{DEC in Micromedia}{Cégep de Rimouski}{}{}{Specialisation in Office Systems Technology: Micropublishing and Hypermedia}

\section{Master thesis}
\cvitem{Title}{\emph{Beyond the territory : Spaces and geosymbols of sexual diversity}}
\cvitem{Supervisors}{Professor Caroline Desbiens, Professor Marie-Hélène Vandersmissen}
\cvitem{Description\\\emph{(Temporary)}}{The goal of this research is to draw a portrait of the numerous geosymbols used in the queer urban spaces, particularly in the cities of Montreal and Quebec city, while criticizing the use of the concept of territory by cultural geography.}

\section{Experience}
\subsection{Vocational} % (fold)
\label{sub:vocational}
\cventry{September 2014\\to today}{Teaching assistant}{Geography department - Université Laval}{Quebec city}{Quebec}{Correcting assignments and exams. Accompanying and supervising students during field work.}
\cventry{November 2013}{Note-taker}{Réseau Villes Région Monde}{Quebec city}{Quebec}{Note-taking during researchers' presentations. Preparing a congress report.\newline{}}
% subsection vocational (end)
\subsection{Miscellaneous} % (fold)
\label{sub:miscellaneous}
\cventry{October 2013\\to July 2015}{Barman}{Bar-Coop l'AgitéE}{Quebec city}{Quebec}{Bartending. Operating AzBar's system. Busing.\newline{}}
\cventry{October 2013\\to October 2014}{Communications coordinator}{Bar-Coop l'AgitéE}{Quebec city}{Quebec}{Developing a communication plan. Coordinate a committee of volunteers working on publicity.\newline{}}

\cventry{August 2007\\to September 2013}{Key-holder / clerk}{Dollarama}{Quebec city}{Quebec}{Managing daily schedules and tasks. Assisting the manager. Customer service. Placing merchandises.\newline{}}
\cventry{July 2012\\to August 2012}{Geomatics technician / intern}{Ville de Québec, arrondissement de Beauport}{Quebec city}{Quebec}{Updating the geospatials database of the district's road network with ArcGIS. Creating specific maps for the contractors working for the district. Make an inventory of miscellaneous municipal equipments and infrastructures.\newline{}}
\cventry{March 2010\\to May 2010}{Administrative Agent}{Centre de Santé et de Services Sociaux Rimouski-Neigette}{Rimouski}{Quebec}{Updating human resources' databases. Miscellaneous administrative tasks.\newline{}}
% subsection miscellaneous (end)



\section{Skills}
%\subsection{Geography}
%\cvcomputer{Intérêts de recherche}{Queer theory, semiotics, urban space, marginality}{Mastered softwares}{ArcGIS, QGIS, MapInfo}
%\cvcomputer{Domaines de la géographie prévilégiés}{Queer geography cultural geography, Urban geography, GIS}{}{}

\subsection{Computer skills}
\cvcomputer{GIS}{ArcGIS, QGIS, GIS Cloud, MapInfo}{CADQAS}{RQDA, Sonal}
\cvcomputer{Office softwares}{Microsoft Office, LibreOffice, \LaTeX.}{Other}{Systat, GNU/Linux, Windows, Photoshop, Illustrator, InDesign, QuarkXpress}

\subsection{Languages}
\cvlanguage{French}{read, talked, written}{}
\cvlanguage{English}{read, talked, written}{}
\cvlanguage{Spanish}{notions}{}

\section{Volunteering} % (fold)
\label{sec:volunteering}
\cventry{October 2014\\to today}{Permanences}{Librairie autogérée la Page Noire}{Quebec city}{Quebec}{}
\cventry{September 2015}{Events, logistics and decoration}{Fête arc-en-ciel}{Quebec city}{Quebec}{}
\cventry{August 2015}{Logistics}{Anniversaire de Craque-Bitume}{Quebec city}{Quebec}{}
\cventry{2013\\to 2014}{Computer reparations and assistance}{Maison des jeunes l'Antidote}{Quebec city}{Quebec}{}

% section volunteering (end)

\section{Publications} % (fold)
\label{sec:publications}
\begin{itemize}
	\item VACHON, Frédéric (2014) \emph{Diversité sexuelle dans la ville de Québec : cartographie des lieux urbains GLBT en contexte francophone}. B.Sc. Memoir. Université Laval, Quebec city.
	\item DURETTE, Maude  \& Frédéric VACHON (2013) \emph{La mesure et l'analyse du mouvement. Synthèse du 5e Forum VRM sur les méthodologies innovantes en études urbaines.} Congress report. Colloque Ville Région Monde, Quebec city.
\end{itemize}
% section publications (end)

\section{Interests}
\cvline{Political}{Participation in two collectives : la Page Noire, a self-managed library and Subvercité, an anti-capitalist collective.}
\cvline{Hobbies}{Reading science-fiction or political essays, cyclism, Linux, vegetarism.}

\end{document}
